### 2015-11-22 2000/abstract.tex
Moving source of 2000 paper

Then we defined algorithms for synchronization using our algebra and
created an implementation which was tested on various filesystems. This
method turned out to be an effective way to create the specification of a
synchronizer since it simplified both the definition and the
implementation.

The methods used in the proofs for soundness and completeness are likely
be usable on other algebras, too. Thus using algebraic approach could make
it possible to extend the synchronizer to other types of datasystems and
to create a general theory of synchronization in the future.

>>>>

Then we defined algorithms for synchronization using our algebra and
created an implementation which was tested on various filesystems. This
method turned out to be an effective way of creating the specification of a
synchronizer since it simplified both the definition and the
implementation.

The methods used in the proofs for soundness and completeness are likely
be usable on other algebras, too. Thus using this algebraic approach could make
it possible to extend synchronization to other types of datasystems and
to create a general theory of synchronization in the future.

### 2015-11-22 2000/ack.tex
Moving source of 2000 paper

%I would like to thank everybody who made it possible for me to write
%this paper. 
I would like to thank my mentor, 
{Norman Ramsey}
%\footnote{Norman Ramsey is a professor at Harvard University (Electrical
%Engineering and Computer Science).}
for offering me such a fascinating project and for giving me a hand when
all the theorems and proofs seemed to be incorrect. I also appreciate the
constructive criticism of my tutor, {Jenny Sendova} 
who was so kind as to read
through the drafts several times and tirelessly untangle my absolutely
confusing complex sentences. I thank {LeeAnn Tzeng} for her remarks
on the paper which helped me a lot to make it more understandable.

>>>>

I would like to thank my mentor, 
{Norman Ramsey}
%\footnote{Norman Ramsey is a professor at Harvard University (Electrical
%Engineering and Computer Science).}
for allowing me to work on such a fascinating project,
and for always being ready to discuss and help me overcome
whatever difficulties I ran into during my work.
I also appreciate the
constructive criticism of my tutor, {Jenny Sendova} 
who kindly read my drafts
several times tirelessly untangling my 
sentences fraugh with overcomplicated grammar.
I thank {LeeAnn Tzeng} for her remarks
on the paper which helped to make it more accessible.

### 2015-11-22 2000/algorithm.tex
Moving source of 2000 paper

In this section we provide an algorithm for reconciliation. The reconciler
algorithm takes sequences leading from the original filesystem to the
replicas (\(S_1, S_2, \ldots S_n\)) and creates sequences of commands for
each replica \(S_1^*, S_2^*, \ldots S_n^*\) which make the
filesystems as close as possible. 
%%%\(S_i^*\) contains all
%%%non--conflicting commands from \(S_1, S_2, \ldots S_n\) which is not
%%%already applied to \(S_i\). 
%%%\begin{notrsi}
%%%We also would like to be sure that if there
%%%are no conflicting commands, then after synchronization, all replicas
%%%should be the same.
%%%\end{notrsi}

%%%Thus, 
When creating the algorithm, we keep in mind the following:\\
\emph{a command 
\(C\in {S}_1\cup{S}_2\cup\ldots\cup{S}_n\) 
should be propagated to replica \(R_i\) iff:}
\begin{itemize}
\item \(C\) is not already applied to \(R_i\)
\item there are no conflicts on command \(C\)
\item there are no conflicts on any command which must precede \(C\) 
\end{itemize}

\medskip
{\small{
Why do we need the last criterion? Consider the following case: in the
original replica we had \(O(\pi)=\cfile{X}\). 
We modified replica \(A\) with the following
commands: \(edit(\pi,\cdir{Y}); create(\pi\cdot p,\cfile{W})\).
Replica \(B\) was modified by the command \(edit(\pi,\cfile{Z})\).
Now \(edit(\pi,\cdir{Y})\) and \(edit(\pi,\cfile{Z})\) are
conflicting commands, so we cannot apply \(edit(\pi,\cdir{Y})\) to replica
\(B\). But that way, we cannot propagate
\(create(\pi\cdot p,\cfile{W})\) to it either.
\remark{However, if \(O(\pi)\) was a directory, it could be.}
}}\medskip

%We also need to determine which commands must precede another
%one. Clearly
A
command \(C_1\) must precede command \(C_2\) iff 
\(\neg(C_1; C_2\eqifnbr C_2; C_1)\), it originally preceded \(C_2\),
and they appear in the same sequence \(S_i\). 
%Note that we define this property only
%if \(C_1\) and \(C_2\) are from the same sequence since otherwise they
%would be conflicting commands.

Now, in order to preserve the order of commands in sequences 
\(S_1, S_2, \ldots S_n\), we define the algorithm as follows:
\begin{notrsi}
\\
\emph{To determine \(S_i^*\):}
\begin{enumerate}
\item Detect conflicting commands between sequences
\item Detect must--follow conflicting commands
\item Omit these commands from all sequences
\item Omit commands in \(S_i\) from all other sequences
\item Define \(S_i^*\) as 
\(S_1; S_2; \ldots S_{i-1}; S_{i+1}; \ldots S_n\)
\end{enumerate}
Or, more formally:
\end{notrsi}
\begin{alltt}
FOR every sequence \(S\sb{i}\)
  FOR each command \(C\in S\sb{i}\)  
    FOR every sequence \(S\sb{j}\)
      IF \(C\) should be propagated to replica \(R\sb{j}\) THEN
        append \(C\) to \(S\sb{j}\sp{*}\).
\end{alltt}

We can get the sequence of conflicting commands using a similar
algorithm. The reconciler produces two sequences for every replica: the
first one (\(S_i^*\)) can be applied to the replica immediately, while
the second one (conflicting commands, \(S_i^C\)) needs the user's or
other algorithms' help to be resolved.

>>>>

In this section we provide an algorithm for reconciliation. The reconciler
algorithm takes the sequences leading from the original filesystem to the
replicas (\(S_1, S_2, \ldots S_n\)) and creates sequences of commands for
each replica \(S_1^*, S_2^*, \ldots S_n^*\) which make the
filesystems as close as possible.

When creating the algorithm, we keep in mind the following:\\
\emph{a command 
\(C\in {S}_1\cup{S}_2\cup\ldots\cup{S}_n\) 
should be propagated to replica \(R_i\) iff:}
\begin{itemize}
\item \(C\) is not already applied to \(R_i\)
\item there are no conflicts on command \(C\)
\item there are no conflicts on any command which must precede \(C\) 
\end{itemize}

\medskip\noindent{\small{
Why do we need the last criterion? Consider the following case: in the
original replica we had \(O(\pi)=\cfile{W}\). 
We modified replica \(A\) with the following
commands: \(edit(\pi,\cdir{X}); create(\pi\cdot p,\cfile{Z})\).
Replica \(B\) was modified by the command \(edit(\pi,\cdir{Y})\).
A third replica \(C\) was not modified.
Now \(edit(\pi,\cdir{X})\) and \(edit(\pi,\cdir{Y})\) are
conflicting commands. \(create(\pi\cdot p,\cfile{Z})\) has no conflicts.
Although we could propagate this \(create\) to replica \(B\), we
cannot apply it to replica \(C\) as we would not know whether to apply
\(edit(\pi,\cdir{X})\) from \(A\) or \(edit(\pi,\cdir{Y})\) from \(B\) to
it. I thank Bill Zissimopoulos for calling my attention to the third
condition in the reconciliation algorithm. --- EC, 2015
}}\medskip

A command \(C_1\) must precede command \(C_2\) iff 
\(C_1; C_2\neqifnbr C_2; C_1\), it originally preceded \(C_2\),
and they appear in the same sequence \(S_i\). 
%Note that we define this property only
%if \(C_1\) and \(C_2\) are from the same sequence since otherwise they
%would be conflicting commands.

Now, in order to preserve the order of commands in sequences 
\(S_1, S_2, \ldots S_n\), we define the reconciliation algorithm as follows:
\begin{notrsi}
\\
\emph{To determine \(S_i^*\):}
\begin{enumerate}
\item Detect conflicting commands between sequences
\item Detect commands which must follow conflicting commands
\item Omit these commands from all sequences
\item Define \(S_i^*\) as 
\(S_1; S_2; \ldots S_{i-1}; S_{i+1}; \ldots S_n\)
\end{enumerate}
Or, more formally:
\end{notrsi}
\begin{alltt}
FOR every sequence \(S\sb{i}\)
  FOR each command \(C\in{S}\sb{i}\)  
    FOR every sequence \(S\sb{j}\)
      IF \(C\) should be propagated to replica \(R\sb{j}\) THEN
        append \(C\) to \(S\sb{j}\sp{*}\).
\end{alltt}

We can get sequences of conflicting commands using a similar
algorithm. This way the reconciler can produce two sequences for every replica: the
first one (\(S_i^*\)) can be applied to the replica immediately, while
the second one containing the conflicting commands (\(S_i^C\)) needs the user's or
other algorithms' help to be resolved.
